What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
topic extraction section edit

\subsection{Topic and Concept Extraction}
Topic extraction, sometimes called concept extraction, uses tools such as Latent Dirichlet Allocation (LDA)~\cite{Blei2003} and Latent Semantic Indexing (LSI) to extract
independent word distributions (topics) from
	documents (commit log comments). Many researchers~\cite{marcus04wcre,Poshyvanyk2007,lukins08wcre,Linstead2007} have applied tools like LSI and LDA for mining repositories, in particular analyzing source code, bugs or developer comments.
\begin{comment}
Ideally these extracted topics 
correlate with actual development topics that the developers discussed
during the development of the software project. For example, our technique might identify a collection of words: ``list next has iterator add'', which we then identify (manually) as concerning the topics of collections and the Iterator pattern.
\end{comment}

@@

One issue that arises with use of unsupervised techniques is how to label the topics. While the topic models themselves are generated automatically, what to make of them is less clear. For example, in our previous work~\cite{Hindle09ICSM}, and in \cite{Baldi2008}, topics are named manually: human experts read the highest-frequency members of a topic and assign a keyword accordingly. E.g., for the word list ``listener change remove add fire'', Baldi et al. assign the keyword \emph{event-handling}. The labels are reasonable enough, but still require some expert in the field to determine them. Our technique is automated, because we match keywords from WordNet to words in the topic model.

>>>>

\subsection{Topic and Concept Extraction}
Topic extraction, sometimes called concept extraction, uses tools such as Latent Dirichlet Allocation (LDA)~\cite{Blei2003} and Latent Semantic Indexing (LSI) to extract
independent word distributions (topics) from
	documents (commit log comments). Many researchers~\cite{marcus04wcre,Poshyvanyk2007,lukins08wcre,Linstead2007} have applied tools like LSI and LDA for mining software repositories, in particular analyzing source code, bugs or developer comments.
\begin{comment}
Ideally these extracted topics 
correlate with actual development topics that the developers discussed
during the development of the software project. For example, our technique might identify a collection of words: ``list next has iterator add'', which we then identify (manually) as concerning the topics of collections and the Iterator pattern.
\end{comment}

@@

One issue that arises with the use of unsupervised techniques is how to label the topics. While the topic models themselves are generated automatically, what to make of them is less clear. For example, in our previous work~\cite{Hindle09ICSM}, and in \cite{Baldi2008}, topics are named manually: human experts read the highest-frequency members of a topic and assign a keyword accordingly. For example, given the word list ``listener change remove add fire'', Baldi et al. assign the keyword \emph{event-handling}. The labels are reasonable enough, but still require some expert in the field to determine them. Our technique is automated, because we match keywords from WordNet to words in the topic model.
